Wireless service accounting based on Ethereum state channels - Master Thesis

### 2019-10-27 Paper.tex
Add Lluis minor fixes

The consensus mechanism ensures a common order
of unambiguous transactions and
blocks, and guarantees integrity and
blockchain consistency a
through geographically distributed nodes.
By its design, the blockchain has characteristics
such as: decentralization, integrity and audibility.
The blockchain can serve as a new
type of software connector, which should be considered
as a possible decentralized alternative to storage
of existing centralized shared data.

@@

In addition, depending on the different levels of
access permission, block chains can
split into two types:
1) public (such as Bitcoin and Ethereum); and
2) private (such as Hyperledger). Blockchain serves
as a platform for smart contracts
(hereinafter, \textit{smart contracts}).
For example, programmed in the Solidity language of
Ethereum, stay and run.
Blockchain is a technology concept
DLT distributed ledger
(\textit{distributed ledger technology}).
It can be integrated into multiple business areas.

@@

\paragraph{\texttt{closeChannel}} Accepts the amount of ETH to refund
to sender, the \texttt{channelId} and the \texttt{signature} of the
payer; checks the signature and after updating the state, transfers
the amount to the owner of the contract and the return to the channel
opener.

@@

During development and in order to ease
the automatic deployment of the contract
over a Truffle's suite Ganache-CLI\cite{ganache}
instance there are two until scripts on the
repository\cite{state-channel-contract-a}
\texttt{utils/compile.js} and \texttt{utils/deploy.js}
that take care of merging all the Solidity source
code required and deploying it to the Ganache instance.

>>>>

The consensus mechanism ensures a common order
of unambiguous transactions and
blocks, and guarantees integrity and
blockchain consistency
through geographically distributed nodes.
By its design, the blockchain has characteristics
such as: decentralization, integrity and audibility.
The blockchain can serve as a new
type of software connector, which should be considered
as a possible decentralized alternative to storage
of existing centralized shared data.

@@

In addition, depending on the different levels of
access permission, block chains can
split into two types:
1) public (such as Bitcoin and Ethereum); and
2) private (such as Hyperledger). Blockchain serves
as a platform for smart contracts
(hereinafter, \textit{smart contracts}).
For example, programmed in the Solidity language of
Ethereum that are able to be compiled into Ethereum
Virtual Machine bytecode and run over this EVM.
Blockchain is a technology concept
DLT distributed ledger
(\textit{distributed ledger technology}).
It can be integrated into multiple business areas.

@@

\paragraph{\texttt{closeChannel}} Accepts the amount of ETH to
transfer to the contract owner, the channelId and the signature of the
payer; checks the signature, calculates the non used purchase value
and, after updating the state, transfers both the amount to the owner
of the contract, and the return to the channel opener

@@

During development and in order to ease
the automatic deployment of the contract
over a Truffle's suite Ganache-CLI\cite{ganache}
instance there are two util scripts on the
repository\cite{state-channel-contract-a}
\texttt{utils/compile.js} and \texttt{utils/deploy.js}
that take care of merging all the Solidity source
code required and deploying it to the Ganache instance.
